|

### 2025-01-22 doc/paper.qmd
refinement

4. **Rank the following factors in order of importance when evaluating earnings announcements (i = most important, v = least important):**
    i) Earnings per share (EPS) compared to analyst forecasts
    ii) Revenue growth
    iii) Management guidance and commentary
    iv) Market reaction on the day of the announcement
    v) Industry trends and macroeconomic conditions

>>>>

4. **Rank the following factors in order of importance when evaluating earnings announcements (1 = most important, 5 = least important):**
    * Earnings per share (EPS) compared to analyst forecasts
    * Revenue growth
    * Management guidance and commentary
    * Market reaction on the day of the announcement
    * Industry trends and macroeconomic conditions
